A thermodynamic view of dusty protoplanetary disks

### 2017-07-01 paper.tex
tweaked intro to fit restructure

%\title{On the entropy of 
%  isothermal dusty gas: application to protoplanetary disks}  
\title{A thermodynamic view of dusty protoplanetary disks}
 % \title{Dust-free modeling of dusty protoplanetary disks I:
%axisymmetric stability}
\author{Min-Kai Lin\altaffilmark{1,2,3}}
\author{Andrew N. Youdin\altaffilmark{1}}
%\affil{Department of Astronomy and Steward Observatory, 
%University of
 % Arizona, Tucson, AZ 85721, USA\\
%Institute of Astronomy and Astrophysics, Academia Sinica, 
%Taipei 10617, Taiwan}
\altaffiltext{1}{Department of Astronomy and Steward Observatory, 
University of
Arizona, Tucson, AZ 85721, USA}
\altaffiltext{2}{Steward Theory Fellow}
\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
Taipei 10617, Taiwan
}
\email{mklin@asiaa.sinica.edu.tw}

>>>>

%\title{On the entropy of 
%  isothermal dusty gas: application to protoplanetary disks}  
\title{A thermodynamic view of dusty protoplanetary disks}
 % \title{Dust-free modeling of dusty protoplanetary disks I:
%axisymmetric stability}
\author{Min-Kai Lin\altaffilmark{1,2,3}}
\author{Andrew N. Youdin\altaffilmark{2}}
%\affil{Department of Astronomy and Steward Observatory, 
%University of
 % Arizona, Tucson, AZ 85721, USA\\
%Institute of Astronomy and Astrophysics, Academia Sinica, 
%Taipei 10617, Taiwan}
\altaffiltext{1}{Institute of Astronomy and Astrophysics, Academia Sinica, 
Taipei 10617, Taiwan
}
\altaffiltext{2}{Department of Astronomy and Steward Observatory, 
University of
Arizona, Tucson, AZ 85721, USA}
\altaffiltext{3}{Steward Theory Fellow}
\email{mklin@asiaa.sinica.edu.tw}
